Automated Topic Naming

### 2011-09-05 ese/ese.tex
46% through and not a lot of problems

Concrete applications of topics and \emph{labelled topic extraction}
range from project dashboards to annotating software artifacts such as revisions and bug reports with
NFR-related tags.
Project dashboard~\cite{dashboard} are typically employed by managers and are used to
provide quick summaries of the effort put into a software project. In this case, 
labelled topic extraction would allow managers to track effort
related to NFR topics, such as portability.
These techniques also allow for the annotation of commit comments
 and other software artifacts with NFRs. 
This would enable querying of bug reports and artifacts by relevant NFRs. 
For instance a manager can confirm if their developers were
focused on \emph{usability} by looking for
 \emph{usability}-relevant revisions and bug reports.

@@

\section{Study Design and Execution}
Figure \ref{fig:process} gives an outline of our methodology.
We began by gathering source data and creating topic models. For semi-unsupervised labelling, we generated three sets of word-lists as signifiers for NFRs.
%e created labels using a well-known NFR taxonomy. 
In supervised learning, we trained our data with manual annotations in order to match topics with NFRs. Finally, these topics were used to analyze the
role of NFRs in software maintenance.

@@

ROC values provide a score %, similar to school letter-grades (A is 0.9, C is 0.6),
 reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false
positive rate (1 - specificity). 
A perfect learner has a ROC value of 1.0, reflecting perfect recall and precision. 
A ROC result of 0.5 would be equivalent to a random learner (that is, issuing as many false positives as true positives). 
The %area under the -- NE confusing to have area again ... and not importantana
ROC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen
negative instance.
We consider our labelling classifiers acceptable if they outperform a random classifier (0.5).

@@

Our second word-list, \textsf{exp2}, uses the ISO9126 taxonomy described above (Section \ref{sec:wordlist}) to seed the word-lists.
%We use these qualities later on as classes in supervised labelling. NE confusing the issue here, I think.
The terms from ISO9126 may not capture all words occurring in the topics that are nonetheless associated with one of the NFRs. 
For example, the term ``redundancy'' is one 
we considered to be
relevant to discussion of \emph{reliability}, but is not in the standard. 
We therefore took the NFRs from the ISO9126 and added to them.

>>>>

Concrete applications of topics and \emph{labelled topic extraction}
range from project dashboards to annotating software artifacts such as revisions and bug reports with
NFR-related tags.
Project dashboards~\cite{dashboard} are typically employed by managers and are used to
provide quick summaries of the effort put into a software project. In this case, 
labelled topic extraction would allow managers to track effort
related to NFR topics, such as \emph{portability}.
These techniques also allow for the annotation of commit comments
 and other software artifacts with NFRs. 
This would enable querying of bug reports and artifacts by relevant NFRs. 
For instance a manager can confirm if their developers were
focused on \emph{usability} by looking for
 \emph{usability}-relevant revisions and bug reports.

@@

\section{Study Design and Execution}
Figure \ref{fig:process} gives an outline of our methodology.
We began by gathering source data and creating topic models. For semi-unsupervised labelling, we generated three sets of word-lists as signifiers for NFRs.
%e created labels using a well-known NFR taxonomy. 
With supervised learning, we trained our data with manual annotations in order to match topics with NFRs. Finally, these topics were used to analyze the
role of NFRs in software maintenance.

@@

ROC values provide a score %, similar to school letter-grades (A is 0.9, C is 0.6),
 reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false
positive rate (1 - specificity). 
A perfect learner has a ROC value of $1.0$, reflecting perfect recall and precision. 
A ROC result of $0.5$ would be equivalent to a random learner (that is, issuing as many false positives as true positives). 
The %area under the -- NE confusing to have area again ... and not importantana
ROC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen
negative instance.
We consider our labelling classifiers acceptable if they outperform a random classifier (0.5).

@@

Our second word-list, \textsf{exp2}, uses the ISO9126 taxonomy described above (Section \ref{sec:wordlist}) to seed the word-lists.
%We use these qualities later on as classes in supervised labelling. NE confusing the issue here, I think.
The terms from ISO9126 may not capture all words occurring in the topics that are nonetheless associated with one of the NFRs. 
For example, the term ``redundancy'' is one 
we considered to be
relevant to discussion of \emph{reliability}, but is not in the standard. 
We therefore took the NFRs from the ISO9126 and added terms to them.
